---
title: "Gene signature overlap comparisons"
author: Paul J. Myers
output:
  html_document:
    fig_width: 9
    fig_height: 6
    theme: spacelab
    toc: yes
  pdf_document: 
    toc: yes
    fig_width: 12
    fig_height: 9
Date of creation: "11/10/2021"
R version: "4.1.2"
---
# Housekeeping code
```{r Load packages, message=F, warning=F}
### Load packages:
library(tidyverse)
library(magrittr)
library(BiocManager)
library(paletteer)
library(cowplot)
library(ggstatsplot)
library(ggbeeswarm)
library(ComplexHeatmap)
```

```{r Clear workspace}
### Clear R workspace:
rm(list=ls())
```

```{r Check working directory}
### Check that current working directory is correct and the desired one:
cwd <- getwd()
cwd
```

```{r Define ni operator}
## Define 'not in' (ni) operator
`%ni%` <- Negate(`%in%`)
```

This function can be used to generate a ggplot with a blank grid and black box surrounding the plot area. The only input to the function specifies whether y tick marks and labels are desired or not (depending on the type of plot you are generating).
```{r Custom ggplot theme for plot background}
theme_cust <- function(ticks=T, axis="y", box=T, lnsz=1,
                       xtickangle=0, hjust=NULL, vjust=NULL, fill=NA,
                       legend.position="right"){
  theme_out <- theme(legend.position=legend.position)
  if (ticks == FALSE & axis == "y" ){
    theme_out <- theme_out + theme(
      axis.text.y = element_blank(), axis.ticks.y = element_blank(), # Make y axis ticks blank
      axis.line.y = element_blank(),
      axis.line.x = element_blank(),
      panel.background = element_rect(size = lnsz, color = "black", fill = fill),
      )
  } else if (ticks == FALSE & axis != "y"){
    theme_out <- theme_out + theme(
      axis.text.x = element_blank(), axis.ticks.x = element_blank(), # Make x axis ticks blank
      axis.line.y = element_blank(),
      axis.line.x = element_blank(),
      panel.background = element_rect(size = lnsz, color = "black", fill = fill),
      )
  } else {
     theme_out <- theme_out + theme(
       axis.line.y = element_blank(),
       axis.line.x = element_blank(),
       panel.background = element_rect(size = lnsz, color = "black", fill = fill),
       axis.text.x = element_text(angle=xtickangle, hjust = hjust, vjust=vjust),
       ) 
  }
  
  if (xtickangle==90){
    theme_out <- theme_out + theme(axis.text.x = element_text(angle=xtickangle, hjust = 1, vjust=0.4))
  }
  
  if (box != TRUE) {
    theme_out <- theme_out + theme(panel.background = element_blank(),
                                   axis.line.y = element_line(size = lnsz, color = "black"),
                                   axis.line.x = element_line(size = lnsz, color = "black")
                                   )
  } else {
    theme_out <- theme_out
  }
  return(theme_out)
}

# Julia's Plots.jl default color order:
julia_cols <- c("#009AFA","#E26E47","#3FA54E","#c270D2","#AD8F18","#01ABAE","#ED5F92","#C68324","#01A98C","#8F961E","#01A9CD","#9B7EE8","#618CF7","#F16072","#DC65B7","#6D9E33")
```


# Gene signatures of interest
Here we introduce the "HIF signature" -- a set of 44 HIF target genes that were described/used by [Li et al. (2014)](https://doi.org/10.1038/nature13557).
```{r HIF signature}
hif.sig <- c("IGFBP3", "EDN2", "PFKFB4", "FLT1", "TFR2", "BNIP3L", "TGFA","BNIP3","PGK1","EGLN1","LDHA","EGLN3","CP","TGFB3","PFKFB3",
             "HK1","TFRC","EDN1","CDKN1A","CA9","ADM1","HMOX1","SERPINE1","LOX","NDRG1","CA12","PDK1","VEGFA","ERO1L","RORA","P4HA1","MXI1",
             "SLC2A1","STC2","MIF","DDIT4","ENO1","CXCR4","PLOD1","P4HA2","GAPDH","PGAM1","TMEM45A","PIM1")


```


We will also look at the immune and stromal signatures that underpin the ESTIMATE algorithm [(Yoshihara et al., 2013)](https://doi.org/10.1038/ncomms3612) and see how their enrichment compares to the enrichment of the pcEMT signature (as well as how much overlap there is between pcEMT and these signatures).
```{r ESTIMATE immune and stromal signatures, message=F}
fn.estimate_sigs <- "ESTIMATE_immune_stromal_signatures.txt"
est.sig <- read_tsv(fn.estimate_sigs)

est_strom <- est.sig %>% filter(type=="Stromal") %>% pull(gene)
est_imm <- est.sig %>% filter(type=="Immune") %>% pull(gene)

est_sigs <- list(ESTIMATE_IMMUNE_SIGNATURE = est_strom,
                  ESTIMATE_STROMAL_SIGNATURE = est_imm) # list for GSVA calculations

```


```{r pcEMT signature, warning=F, message=F}
## Load pan-cancer EMT signature:
pcemt.fn <- "Pan-cancer-EMT-signature_Mak-et-al-2016.txt"
pcemt.sig <- read_tsv(pcemt.fn, col_names = c("gene","type"))
pcemt.sig.m <- read_tsv(pcemt.fn, col_names = c("gene","type")) %>% subset(type %in% "M")

```

```{r Collisson signature, message=F}
## Load PDAssigner gene list:
fn.sub <- "pdassigner_genes.csv"
pda_genes <- read_csv(fn.sub)
subtype_anno <- pda_genes[,-1] %>% data.frame()
rownames(subtype_anno) <- pda_genes$gene

pda_class <- pda_genes %>% filter(type=="classical") %>% dplyr::pull(gene)
pda_exo <- pda_genes %>% filter(type=="exocrine_like") %>% dplyr::pull(gene)
pda_qm <- pda_genes %>% filter(type=="QM") %>% dplyr::pull(gene)
pda_sigs <- list(COLLISSON_CLASSICAL = pda_class,
                 COLLISSON_EXOCRINE = pda_exo,
                 COLLISSON_QUASIMESENCHYMAL = pda_qm)
```

```{r PDAC signatures, message=F}
## =============== Load the Collisson, Moffitt, and Bailey signatures =============== ##\
# -- Collisson:
fn.coll <- "pdassigner_genes.csv"
coll.sig <- read_csv(fn.coll) %>% 
  mutate(sig = paste0("Collisson ",type))
coll_anno <- coll.sig[,-1] %>% data.frame() 
rownames(coll_anno) <- coll.sig$gene

# -- Moffitt:
fn.mof <- "Moffitt_PDAC_signature.txt" # PDAC subtype signature
fn.mof_strom <- "Moffitt_stromal_signature.txt" # stromal signature
mof.sig <- read_tsv(fn.mof) %>% 
  mutate(sig = paste0("Moffitt ",type))
mof_strom.sig <- read_tsv(fn.mof_strom) # Moffitt stromal signature

# -- Bailey:
fn.bail <- "BaileySubtypeSig.csv"
bail.sig <- read_csv(fn.bail) %>% 
  mutate(
    gene = Symbol,
    type = "Bailey",
    sig = "Bailey"
    ) %>% 
  dplyr::select(gene, type, sig)

# -- Combine them:
pdac.sigs <- rbind(coll.sig, mof.sig, bail.sig)
```

```{r Bailey gene programmes and differentially expressed genes}
library(readxl)
## ======= Load the gene programmes defining the Bailey PDAC subtypes and format into dataframe ======= ##
gp_names <- excel_sheets("Bailey_et_al_TableS16.xlsx")  # names of gene programmes

gps <- data.frame() # initialize dataframe
for(i in 1:length(gp_names)){
  gpi = read_xlsx("Bailey_et_al_TableS16.xlsx", sheet=i)
  genesi = paste(gpi$Nodes, collapse=",") %>% strsplit(",") %>% .[[1]]
  dfi = data.frame(gene=genesi, gp=gp_names[i], type="") %>% unique()
  gps = rbind(gps, dfi)
  if(i==1){ # if GP1, duplicate for immunogenic and progenitor subtypes
    gps = gps %>% mutate(type = case_when(str_detect(gp,"1") ~ "Progenitor", T ~ type))
    dfi2 = data.frame(gene=genesi, gp=gp_names[i], type="Immunogenic") %>% unique()
    gps = rbind(gps, dfi2)
  }
}
gps <- gps %>% 
  mutate(
    type = case_when(str_detect(gp,"2|3|4|5") ~ "Squamous",
                     str_detect(gp,"6|7|8") ~ "Immunogenic",
                     str_detect(gp,"9|10") ~ "ADEX",
                     T ~ type
                     )
  )


## ======= Load differentially expressed genes from SAM analysis and label with subtype ======= ##
# -- Load genes from SAM analysis:
sam <- read_tsv("Bailey_sam_analysis_genes.txt")


# -- Load genes from one-versus-rest DGE analyses and keep if in SAM analysis gene list:
dge <- read_tsv("Bailey_subtype_DGE.txt") %>% 
  filter(ensemblID %in% sam$ensemblID)  # keep only genes from SAM analysis


# -- Define Bailey signature from DGE list:
bail.sig2 <- dge %>% 
  dplyr::select(-ensemblID) %>% 
  dplyr::rename(gene = symbol) %>% 
  mutate(sig = paste0("Bailey ", type))

pdac.sigs2 <- rbind(coll.sig, mof.sig, bail.sig2)
```


```{r Compare PDAC gene signature overlaps}
## Intersecting genes with pcEMT signature:
pcemt_intergenes <- intersect(pcemt.sig$gene, pdac.sigs$gene)

# -- Plot of intersecting/overlapping genes w/ pcEMT signature:
colors1 <- paletteer_d("RColorBrewer::Set1")[3:4] # colors for plot
sigs_df <- pcemt.sig %>% 
  mutate(sig = paste0("pcEMT-",type),
         type = case_when(type=="M" ~ "Mesenchymal",
                          type=="E" ~ "Epithelial",
                          T ~ type),
  ) %>% 
  rbind(pdac.sigs) %>% 
  mutate(sig = case_when(sig=="Collisson classical" ~ "Collisson Classical",
                         sig=="Collisson exocrine_like" ~ "Collisson Exocrine-like",
                         T ~ sig
                         ),
         )

w1 = 3
h1 = 1.5
sigs_df %>% 
  filter(gene %in% pcemt_intergenes) %>% 
  filter(!str_detect(sig,"pcEMT-M|pcEMT-E")) %>% 
  mutate(pcEMT_sig = gene %>% match(pcemt.sig$gene) %>% pcemt.sig$type[.],
         pcEMT_sig = case_when(pcEMT_sig=="M" ~ "Mesenchymal",
                          pcEMT_sig=="E" ~ "Epithelial",
                          T ~ pcEMT_sig),
         sig = str_to_title(sig),
         ) %>% 
  arrange(pcEMT_sig) %>% 
  mutate(gene = factor(gene, levels=unique(gene)),
         # sig = factor(sig, levels=c("Bailey Squamous","Bailey Progenitor","Collisson Classical")),
         ) %>% 
  ggplot(aes(x=gene, y=sig, fill=pcEMT_sig)) + 
    geom_tile(color="black", size=0.8) +
    scale_fill_manual(values=colors1) +
    theme_minimal_grid(8, rel_small=1, rel_large=1, rel_tiny=1) + #panel_border(size=1, color="black") +
    theme(axis.text.x=element_text(angle=90, vjust=0.4, hjust=1))+
    labs(x="Gene symbol", y="PDAC signature", title="Overlapping pcEMT and\nPDAC signature genes", fill="pcEMT signature")
ggsave("pcEMT-PDAC-sig_gene-overlaps.png", width=w1, height=h1)
ggsave("pcEMT-PDAC-sig_gene-overlaps.pdf", width=w1, height=h1)
         

## ------------------- ggupset ----------------------- ##
library(ggupset)
lt <- sigs_df %>% 
  dplyr::select(gene, sig) %>% 
  mutate(value = TRUE) %>% 
  pivot_wider(names_from=gene, values_from=value, 
              values_fn = function(x){if(x){TRUE} else {FALSE}}
              ) %>% 
  data.frame()
lt[is.na(lt)] <- F # fill NAs with FALSE values
  
df4upset <- lt %>% 
  gather(gene, member, -sig) %>% 
  filter(member) %>% 
  dplyr::select(-member) %>% 
  distinct() %>% 
  group_by(gene) %>% 
  summarise(sig = list(sig))


# -- Upset plot:
w2 = 4.2 # 6
h2 = 3 # 4.5
ymax = 620
gs_upset <- df4upset %>% 
  ggplot(aes(x=sig)) +
    geom_bar() +
    geom_text(stat='count', aes(label=after_stat(count)), vjust=-1, size=2.5) +
    scale_x_upset(order_by = "degree") +
    scale_y_continuous(lim=c(0,ymax)) +
    theme_combmatrix(
      combmatrix.label.height=unit(h2/2.5, "in"),
      # combmatrix.panel.margin=unit(c(0.5, 0.5), "pt"),
      combmatrix.panel.point.size=1,
      combmatrix.panel.line.size=0.5,
      ) +
    theme(text=element_text(size=8), axis.text.y=element_text(size=8), title=element_text(size=7, face="bold")) +
      labs(x="", y="Number of unique genes", title="pcEMT and PDAC signature overlaps")
gs_upset
ggsave("pcEMT-PDAC-sig_upset-plot.png", plot=gs_upset, width=w2, height=h2)
ggsave("pcEMT-PDAC-sig_upset-plot.pdf", plot=gs_upset, width=w2, height=h2)
```



# MSigDB gene sets
Here we load the necessary packages and gene sets from/related to the Molecular Signatures Database (MSigDB) for analyzing pathway and gene set enrichment in downstream analyses.
```{r Load packages and MSigDB collections, message=FALSE, warning=FALSE}
## Load packages:
library(org.Hs.eg.db)
library(msigdbr)


### Define MSigDB gene set collection(s) to use --> retrieve with 'msigdbr' package:
species = "Homo sapiens"
 
## Retrieve Hallmark and canonical pathways collections in the database (C1-H and C2-CP):
hall = msigdbr(species = species, category = "H")
cp = msigdbr(species = species, category = "C2", subcategory = "CP")
cp.b = msigdbr(species = species, category = "C2", subcategory = "CP:BIOCARTA")
cp.r = msigdbr(species = species, category = "C2", subcategory = "CP:REACTOME")
cp.p = msigdbr(species = species, category = "C2", subcategory = "CP:PID")
cp.k = msigdbr(species = species, category = "C2", subcategory = "CP:KEGG")
cp.w = msigdbr(species = species, category = "C2", subcategory = "CP:WIKIPATHWAYS")
gene_sets1 <- rbind(hall, cp, cp.b, cp.r, cp.p, cp.k, cp.w) %>% split(x = .$gene_symbol, f = .$gs_name)

## Go collections (C5):
go.bp <- msigdbr(species = species, category = "C5", subcategory = "GO:BP")
go.cc <- msigdbr(species = species, category = "C5", subcategory = "GO:CC")
go.mf <- msigdbr(species = species, category = "C5", subcategory = "GO:MF")
gene_sets2 <- rbind(go.bp, go.cc, go.mf) %>% split(x = .$gene_symbol, f = .$gs_name)

## Transcription factor target collections:
go.tft <- msigdbr(species = species, category = "C3", subcategory = "TFT:GTRD")
go.tft_leg <- msigdbr(species = species, category = "C3", subcategory = "TFT:TFT_Legacy")
gene_sets3 <- rbind(go.tft, go.tft_leg) %>% split(x = .$gene_symbol, f = .$gs_name)

## Pan-cancer EMT sub-signatures and HIF signature:
pcemt_e.sig <- pcemt.sig %>% subset(type=="E") %>% dplyr::pull(gene)
pcemt_m.sig <- pcemt.sig %>% subset(type=="M") %>% dplyr::pull(gene)

gene_sets4 <- list(PCEMT_EPITHELIAL = pcemt_e.sig,
                   PCEMT_MESENCHYMAL = pcemt_m.sig,
                   HIF_SIGNATURE = hif.sig
                   ) %>% append(est_sigs)

gene_sets_all <- append(gene_sets1, gene_sets2) %>% append(gene_sets3) %>% append(gene_sets4)

```

# Comparisons
```{r pcEMT and Hallmark Hypoxia signatures, warning=F, message=F}
## Merge pcEMT and Hallmark Hypoxia signatures:
hallhyp_sig <- data.frame(gene=gene_sets1$HALLMARK_HYPOXIA, type="Hallmark Hypoxia")
pcemthh_df <- hallhyp_sig %>% 
  # filter(gene %ni% pcemt.sig$gene) %>% 
  rbind(pcemt.sig) %>% 
  mutate(
    type = case_when(type=="M" ~ "pcEMT-M",
                     type=="E" ~ "pcEMT-E",
                     T ~ type)
  )

## Analyze pcEMT/Hallmark Hypoxia gene overlaps:
w1 = 7
h1 = 3
pcemthh_df %>% 
  unique() %>%   
  group_by(gene) %>% 
  add_count(gene) %>% 
  filter(n > 1) %>% 
  ggplot(aes(x=gene, y=type, fill = type)) + 
    geom_tile(color="black", size=0.8) +
    scale_fill_manual(values=colors1) +
    theme_minimal_grid() + #panel_border(size=1, color="black") +
    theme(axis.text.x=element_text(angle=90, vjust=0.4, hjust=1))+
    labs(x="Gene symbol", y="Signature", title="Overlapping pcEMT and Hallmark Hypoxia genes")
ggsave("pcEMT-HallHyp_gene-overlaps.png", width=w1, height=h1)
ggsave("pcEMT-HallHyp_gene-overlaps.pdf", width=w1, height=h1)
         

## ------------------- ggupset ----------------------- ##
library(ggupset)
lt2 <- pcemthh_df %>% 
  dplyr::select(gene, type) %>% 
  mutate(value = TRUE) %>% 
  unique() %>% 
  pivot_wider(names_from=gene, values_from=value)
lt2[is.na(lt2)] <- F # fill NAs with FALSE values
  
df4upset2 <- lt2 %>% 
  gather(gene, member, -type) %>% 
  filter(member) %>% 
  dplyr::select(-member) %>% 
  # distinct() %>% 
  group_by(gene) %>% 
  summarise(type = list(type))

# -- Upset plot:
w2 = 3.1
h2 = 3.3
gs_upset2 <- df4upset2 %>% 
  ggplot(aes(x=type)) +
    geom_bar() +
    geom_text(stat='count', aes(label=after_stat(count)), vjust=-1, size=2.5) +
    scale_x_upset(order_by = "degree") +
    scale_y_continuous(lim=c(0,210)) +
    theme_combmatrix(
      combmatrix.label.height=unit(h2*0.15, "in"),
      # combmatrix.panel.margin=unit(c(0.5, 0.5), "pt"),
      combmatrix.panel.point.size=1,
      combmatrix.panel.line.size=0.5,
      ) +
    theme(text=element_text(size=8), axis.text.y=element_text(size=8), title=element_text(size=7, face="bold")) +
    labs(x="", y="Number of unique genes", title="pcEMT and Hallmark Hypoxia overlaps")
gs_upset2
ggsave("pcEMT-HallHyp_upset-plot.png", plot=gs_upset2, width=w2, height=h2)
ggsave("pcEMT-HallHyp_upset-plot.pdf", plot=gs_upset2, width=w2, height=h2)
```


```{r PDAC and Hallmark Hypoxia signatures, warning=F, message=F}
## Merge pcEMT and Hallmark Hypoxia signatures:
hallhyp_sig <- data.frame(gene=gene_sets1$HALLMARK_HYPOXIA, type="Hallmark Hypoxia")
pdachyp <- sigs_df %>%
  dplyr::select(-type) %>% dplyr::rename(type=sig) %>% 
  filter(!str_detect(type,"pcEMT")) %>%
  rbind(hallhyp_sig)


## Analyze PDAC/Hallmark Hypoxia gene overlaps:
w1 = 7
h1 = 3
pdachyp %>% 
  unique() %>%   
  group_by(gene) %>% 
  add_count(gene) %>% 
  filter(n > 1) %>% 
  ggplot(aes(x=gene, y=type)) + 
    geom_tile(color="black", size=0.8) +
    theme_minimal_grid() + #panel_border(size=1, color="black") +
    theme(axis.text.x=element_text(angle=90, vjust=0.4, hjust=1))+
    labs(x="Gene symbol", y="Signature", title="Overlapping pcEMT and Hallmark Hypoxia genes")
ggsave("PDAC-HallHyp_gene-overlaps.png", width=w1, height=h1)
ggsave("PDAC-HallHyp_gene-overlaps.pdf", width=w1, height=h1)
         

## ------------------- ggupset ----------------------- ##
library(ggupset)
lt2 <- pdachyp %>% 
  dplyr::select(gene, type) %>% 
  mutate(value = TRUE) %>% 
  unique() %>% 
  pivot_wider(names_from=gene, values_from=value)
lt2[is.na(lt2)] <- F # fill NAs with FALSE values
  
df4upset2 <- lt2 %>% 
  gather(gene, member, -type) %>% 
  filter(member) %>% 
  dplyr::select(-member) %>% 
  # distinct() %>% 
  group_by(gene) %>% 
  summarise(type = list(type))

# -- Upset plot:
w2 = 4.5
h2 = 2.6
gs_upset2 <- df4upset2 %>% 
  ggplot(aes(x=type)) +
    geom_bar() +
    geom_text(stat='count', aes(label=after_stat(count)), vjust=-1, size=2.5) +
    scale_x_upset(order_by = "degree") +
    scale_y_continuous(lim=c(0,700)) +
    theme_combmatrix(
      combmatrix.label.height=unit(h2*0.35, "in"),
      combmatrix.panel.point.size=1,
      combmatrix.panel.line.size=0.5,
      ) +
    theme(text=element_text(size=8), axis.text.y=element_text(size=8), title=element_text(size=7, face="bold")) +
    labs(x="", y="Number of unique\ngenes", title="PDAC signature and Hallmark Hypoxia overlaps")
gs_upset2
ggsave("PDAC-HallHyp_upset-plot.png", plot=gs_upset2, width=w2, height=h2)
ggsave("PDAC-HallHyp_upset-plot.pdf", plot=gs_upset2, width=w2, height=h2)
```


```{r KEGG signaling pathways and Hallmark Hypoxia}
## Merge KEGG signaling and Hallmark Hypoxia signatures:
kegghyp <- gene_sets1 %>% 
  subset(str_detect(names(.), "KEGG_|HALLMARK_HYPO")) %>% 
  subset(str_detect(names(.),"SIGNALING_PATHWAY|HALLMARK_HYPO"))
unsplit_fun <- function(x){
  y = data.frame(type=names(x)[1], gene=x)
  names(y) = c("type","gene")
  return(y)
}

kegghyp_df <- data.frame()
for(i in 1:length(kegghyp)){
  kegghyp_df <- rbind(kegghyp_df, unsplit_fun(kegghyp[i]))
}
kegghyp_df <- kegghyp_df %>% 
  filter(gene %in% kegghyp$HALLMARK_HYPOXIA) %>% 
  mutate(
    type = gsub("KEGG_|_SIGNALING_PATHWAY","",type),
    type = case_when(str_detect(type,"HALLMARK") ~ "Hallmark Hypoxia",
                     T ~ type),
  )

## Analyze KEGG signaling/Hallmark Hypoxia gene overlaps:
w1 = 7
h1 = 3
kegghyp_df %>% 
  unique() %>%   
  group_by(gene) %>% 
  add_count(gene) %>% 
  filter(n > 1) %>% 
  ggplot(aes(x=gene, y=type)) + 
    geom_tile(color="black", size=0.8) +
    # scale_fill_manual(values=colors1) +
    theme_minimal_grid(8) + #panel_border(size=1, color="black") +
    theme(axis.text.x=element_text(angle=90, vjust=0.4, hjust=1), 
          text=element_text(size=8), axis.text.y=element_text(size=8), title=element_text(size=7, face="bold")
          )+
    labs(x="Gene symbol", y="Signature", title="Overlapping KEGG-signaling pathway and Hallmark Hypoxia genes")
ggsave("KEGG-signaling-HallHyp_gene-overlaps.png", width=w1, height=h1)
ggsave("KEGG-signaling-HallHyp_gene-overlaps.pdf", width=w1, height=h1)
         

## ------------------- ggupset ----------------------- ##
library(ggupset)
lt2 <- kegghyp_df %>% 
  dplyr::select(gene, type) %>% 
  mutate(value = TRUE) %>% 
  unique() %>% 
  pivot_wider(names_from=gene, values_from=value)
lt2[is.na(lt2)] <- F # fill NAs with FALSE values
  
df4upset2 <- lt2 %>% 
  gather(gene, member, -type) %>% 
  filter(member) %>% 
  dplyr::select(-member) %>% 
  # distinct() %>% 
  group_by(gene) %>% 
  summarise(type = list(type))

# -- Upset plot:
w2 = 5.5
h2 = 4
gs_upset2 <- df4upset2 %>% 
  ggplot(aes(x=type)) +
    geom_bar() +
    geom_text(stat='count', aes(label=after_stat(count)), vjust=-1, size=2.5) +
    scale_x_upset(order_by = "degree",
                  ) +
    scale_y_continuous(lim=c(0,200)) +
    theme_combmatrix(
      combmatrix.label.height=unit(h2*0.65, "in"),
      # combmatrix.panel.margin=unit(c(0.5, 0.5), "pt"),
      combmatrix.panel.point.size=1,
      combmatrix.panel.line.size=0.5,
      ) +
    theme(text=element_text(size=8), axis.text.y=element_text(size=8), title=element_text(size=7, face="bold")) +
    labs(x="", y="Number of unique\ngenes", title="Hallmark Hypoxia overlaps with KEGG signaling pathways")
gs_upset2
ggsave("KEGG-signaling-HallHyp_upset-plot.png", plot=gs_upset2, width=w2, height=h2)
ggsave("KEGG-signaling-HallHyp_upset-plot.pdf", plot=gs_upset2, width=w2, height=h2)
```

